Yeast RNA-seq 48 sample simulation study

### 2018-02-15 datasets/RNA-Seq/yeast48-replicates-benchmarkFDR.Rmd
Add effect size plots; keep ind_cov in ftCols

  sb <- bd %>% buildBench(data=geneExp, parallel = F, 
                          truthCols = "qvalue")
  rowData(sb)$log2FC <- geneExp$effect_size

@@

@@

# metrics = ""TPR"   "FPR"   "TNR"   "FNR"   "rejections"  "FWER"   "rejectprop"
plotsim_average(res10d, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res10d, met="FPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res10d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)

>>>>

  sb <- bd %>% buildBench(data=geneExp, parallel = F, 
                          truthCols = "qvalue",
                          ftCols = "ind_covariate")
  rowData(sb)$log2FC <- geneExp$effect_size

@@

plotEffectSize(de5)
plotEffectSize(de5, DE=FALSE)

@@

plotsim_average(res10d, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res10d, met="FPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res10d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)

plotEffectSize(de10)
plotEffectSize(de10, DE=FALSE)
